% Bibliography section
\ifdraftbib
\begin{thebibliography}{10}
\bibitem{placeholder2025}
T.~B.~Decided, ``Placeholder Reference for Compilation,'' 2025.
\bibitem{surveyWSN}
To~Be~Updated, ``A Survey on Wireless Sensor Networks,'' 2015--2025, placeholder entry.
\bibitem{energyHarvestSurvey}
To~Be~Updated, ``Energy Harvesting in Wireless Sensor Networks: A Survey,'' 2015--2025, placeholder entry.
\bibitem{energyBalSurvey}
To~Be~Updated, ``Energy Balancing and Sharing Strategies in WSN: A Review,'' 2015--2025, placeholder entry.
\bibitem{lyapunovEnergy}
To~Be~Updated, ``Lyapunov Optimization for Energy Management in Networks,'' 2010--2025, placeholder entry.
\bibitem{drlSurvey}
To~Be~Updated, ``Deep Reinforcement Learning for Networked Systems: A Survey,'' 2016--2025, placeholder entry.
\bibitem{aoiSurvey}
To~Be~Updated, ``Age of Information: A Survey and Applications,'' 2017--2025, placeholder entry.
\bibitem{digitalTwinSurvey}
To~Be~Updated, ``Digital Twin for CPS/IoT: Concepts and Applications,'' 2018--2025, placeholder entry.
\bibitem{marketMechanismWSN}
To~Be~Updated, ``Market-based Resource Allocation in Wireless Networks,'' 2008--2025, placeholder entry.
\bibitem{eetor}
To~Be~Updated, ``Energy-Efficient Transfer Opportunistic Routing (EETOR),'' 2019--2025, placeholder entry.
\bibitem{opportunisticInfo}
To~Be~Updated, ``Opportunistic Information Reporting in Networked Systems,'' 2012--2025, placeholder entry.
\bibitem{fairnessAlloc}
To~Be~Updated, ``Fairness-aware Resource Allocation in Wireless Networks,'' 2005--2025, placeholder entry.
\bibitem{paretoFrontier}
To~Be~Updated, ``Pareto Optimality and Frontier Expansion in Networked Systems,'' 2000--2025, placeholder entry.
\bibitem{statTest}
To~Be~Updated, ``Statistical Tests for Paired Comparisons in Networking Experiments,'' 2000--2025, placeholder entry.
\bibitem{bootstrap}
To~Be~Updated, ``Bootstrap Methods for Confidence Intervals,'' 1990--2025, placeholder entry.
\end{thebibliography}
\else
\nocite{placeholder2025}
\bibliographystyle{IEEEtran}
\bibliography{references}
\fi

